This is experiment one in the springer 1 to 3 numbering (originaly called e2)

### 2018-07-27 experiments/e2/writeup/2018_levy-method/2018_levy-method-e1Springer.Rmd
levy start

---
title: "Experiment 2 of 4"
author: "Matt Green"
output:
  html_document:
    toc: yes
    toc_float: true
    mathjax: default
    template: default
    <!--code_folding: show-->
    theme: default
---

```{r "set working directory to 2018_tidy_version", echo=FALSE}
root="/home/matt/wd/vagueness/experiments/e2/writeup/2018_tidy_version"
if (getwd() != root) setwd(root)
```

```{r "load Libraries and source my functions", message=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(tidymodels)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
source('../functions/summarySEwithin2.R')
source('../functions/e2-preprocessing.R')
source('../functions/pretty_coef_table.R')
source('../functions/pretty_coef_plot.R')
```

@@

These are the example instructions:
```{r showInstructions, echo=FALSE}
data.frame(
  vagueness = c("crisp", "crisp", "vague", "vague"),
  number = c('number', 'word', 'number', 'word'),
  example_instruction = c("Choose the square with 6 dots", "Choose the square with the fewest dots", "Choose a square with about 10 dots", "Choose a square with few dots")  
) %>% kable() %>% kable_styling(full_width = F, position = "left", font_size = 11)
```

These are the items:
```{r showItems, echo=FALSE}
data.frame(
  Item = c("1","2","3","4"),
  'Numbers of dots' = c("06:15:24", "16:25:34", "26:35:44", "36:45:54")
) %>% kable() %>% kable_styling(full_width = F, position = "left", font_size = 11)
```

Pre-process the raw data.
```{r preprocessing, echo=FALSE, message=FALSE}
if( !file.exists('e2-data.txt') ) {
  dat <- gatherData() 
  dat <- declareImpossibleRT(dat)
  #dat <- removeImpossibleTrials(dat)
  dat <- subset(dat, select=c(Subject, Trial, Item, c_Itm, discriminability, Instruction, nchar_instr, Vagueness, Number, Order, Quantity, c_Vag, c_Num, c_Ord, c_Qty, NaType, response_category, isBorderline, RT, RT_log))
  write.table(dat, file='e2-data.txt', sep='\t', quote=FALSE, row.names = FALSE)
}
```

```{r}
raw_data <- read.delim('e2-data.txt')
```

```{r}
trim_data <- perSubjectTrim.fnc(data = raw_data[complete.cases(raw_data),], response='RT', subject='Subject', trim = 2.5)$data
```

@@

```{r}
rtdata <- trim_data
```

>>>>

---
title: "This is experiment one in the springer 1 to 3 numbering (originaly called e2)"
author: "Matt Green"
output:
  html_document:
    toc: yes
    toc_float: true
    mathjax: default
    template: default
    <!--code_folding: show-->
    theme: default
---

```{r 'set working directory', echo=FALSE}
root="/home/matt/wd/vagueness/experiments/e2/writeup/2018_levy-method"
if (getwd() != root) setwd(root)
```

```{r 'load Libraries and source my functions', message=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(tidymodels)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
source('summarySEwithin2.R')
source('concatenate_raw_data.R')
source('declare_impossible_rt.R')
source('remove_impossible_trials.R')
source('pretty_coef_table.R')
source('pretty_coef_plot.R')
```

@@

These are the example instructions:
```{r 'showInstructions', echo=FALSE}
data.frame(
  vagueness = c("crisp", "crisp", "vague", "vague"),
  number = c('number', 'word', 'number', 'word'),
  example_instruction = c("Choose the square with 6 dots", "Choose the square with the fewest dots", "Choose a square with about 10 dots", "Choose a square with few dots")  
) %>% kable() %>% kable_styling(full_width = F, position = "left", font_size = 11)
```

These are the items:
```{r 'showItems', echo=FALSE}
data.frame(
  Item = c("1","2","3","4"),
  'Numbers of dots' = c("06:15:24", "16:25:34", "26:35:44", "36:45:54")
) %>% kable() %>% kable_styling(full_width = F, position = "left", font_size = 11)
```

Concatenate the raw data.
```{r, 'Concatenate the raw data'}
dat <- concatenate_raw_data()
dat %>% select(RT, RESPONSE, response_category) %>% summary() 
```

Catch impossible RTs: sticky fingers (RT<=1) and near timeouts (RT>59,998ms)
```{r, 'declare_impossible_rt'}
dat <- declare_impossible_rt(dat)
dat %>% select(RT, RESPONSE, response_category, NaType) %>% summary()
# show the NA trials
dat %>% filter(is.na(RT)) %>% select(RT_original, RESPONSE, NaType, RT, response_category) 
```

```{r, 'write the raw data to file'}
write.table(dat %>% select(Subject, Trial, Item, c_Itm, discriminability, Instruction, nchar_instr, Vagueness, Number, Order, Quantity, c_Vag, c_Num, c_Ord, c_Qty, NaType, response_category, isBorderline, RT, RT_log), file='e2-data.txt', sep='\t', quote=FALSE, row.names = FALSE)
```

Get the raw data.
```{r, 'get the raw data from file'}
raw_data <- read.delim('e2-data.txt')
```

Trim the data.
```{r, 'trim the data'}
trim_data <- perSubjectTrim.fnc(data = raw_data[complete.cases(raw_data),], response='RT', subject='Subject', trim = 2.5)$data
```

@@

```{r, 'select the response time data'}
rtdata <- trim_data
```

```{r, 'plot the distribution of the trimmed data', fig.width=3, fig.height=3}
ggplot(data=rtdata, aes(RT_log)) + geom_density() + theme(aspect.ratio = 1)
```
